{Sparse Mixture Model (with jk-means a special case)}

### 2016-09-01 docs/latex/ver1.tex
sync

\subsection{JK-Means}

With the above general framework, we focus on a special case $\{ u_{1,i},u_{2,i},\ldots u_{\kappa,i}\} \sim \text{ J out of K draws}$ and $\nu_k = 1/\kappa$. We refer this as JK-Means as when $J=1$, this reduces to standard K-means method.

@@

\begin{algorithm}[H]
\caption{EM algorithm for JK-Means}\label{alg:euclid}
\begin{algorithmic}[1]
% \Procedure{Euclid}{$a,b$}\Comment{The g.c.d. of a and b}
% \State $r\gets a\bmod b$
\While{$||\theta^{(s)}-\theta^{(s+1)}||>\epsilon$}%\Comment{We have the answer if r is 0}
\State Maximize over $\{ u_{i,k}\}_k$ by $ \underset{\{u_{i,k}\}_k} {\text{argmax }}\{u_{i,k}  v_{k}\delta_{\theta_{k}}(y_i)\}$ for all $i$; \Comment{\small pick top J out K based on (\ref{marginal_lik})}
\State Compute $ \mathbb{E}(z_{i,k})= \frac{w_{k,i} \delta_{\theta_{k}}(y_i)}{\sum_k w_{k,i} \delta_{\theta_{k}}(y_i)}$ with $w_{k,i} = u_{i,k} v_{k}$; \Comment{E step  based on (\ref{conditional_lik})}
\State Set $\theta^{(s+1)}_{k}= \text{argmax} \sum_{k=1}^{\kappa} \mathbb{E}z_{k,i} \log \delta_{\theta_{k}}(y_i) $ for all $k$ \Comment{M step: obtain MLE based on (\ref{conditional_lik})}
\EndWhile\label{euclidendwhile}
% \State \textbf{return} $b$\Comment{The gcd is b}
% \EndProcedure
\end{algorithmic}
\end{algorithm}

>>>>

\subsection{Estimation}

@@

\begin{algorithm}[H]
\caption{EM algorithm}\label{alg:euclid}
\begin{algorithmic}[1]
% \Procedure{Euclid}{$a,b$}\Comment{The g.c.d. of a and b}
% \State $r\gets a\bmod b$
\While{$||\theta^{(s)}-\theta^{(s+1)}||>\epsilon$}%\Comment{We have the answer if r is 0}
\State Maximize over $\{ u_{i,k}\}_k$ by $ \underset{\{u_{i,k}\}_k} {\text{argmax }}\{u_{i,k}  v_{k}\delta_{\theta_{k}}(y_i)\}$ for all $i$; \Comment{\small pick top J out K based on (\ref{marginal_lik})}
\State Compute $ \mathbb{E}(z_{k,i})= \frac{w_{k,i} \delta_{\theta_{k}}(y_i)}{\sum_k w_{k,i} \delta_{\theta_{k}}(y_i)}$ with $w_{k,i} = u_{i,k} v_{k}$; \Comment{E step  based on (\ref{conditional_lik})}
\State Set $\theta^{(s+1)}_{k}= \text{argmax} \sum_{k=1}^{\kappa} \mathbb{E}z_{k,i} \log \delta_{\theta_{k}}(y_i) $ for all $k$ \Comment{M step: obtain MLE based on (\ref{conditional_lik})}
\State Set $v^{(s+1)}_{k}=  \sum_{i}\mathbb{E}z_{k,i} /  \sum_{i}\sum_{k}\mathbb{E}z_{k,i}$ \Comment{M step: obtain MLE based on (\ref{conditional_lik})}\label{flex_w_step}
\EndWhile
% \State \textbf{return} $b$\Comment{The gcd is b}
% \EndProcedure
\end{algorithmic}
\end{algorithm}

\subsubsection{JK-Means}

With the above general framework, there is a special case $\{ u_{1,i},u_{2,i},\ldots u_{\kappa,i}\} \sim \text{ J out of K draws}$ and $\nu_k = 1/\kappa$. We refer this as JK-Means as when $J=1$, this reduces to standard K-means method. The estimation procedure is the same as above except step \ref{flex_w_step} is skipped.
